---
title: "Call-in Analysis"
author: "ftinawi"
output:
  html_document: default
  pdf_document: default
---

# Call-in/Cancellation Experiment Analysis

**Goal**: Evaluate the performance of the call-in initiative.

### Importing the csv files

```{r}
testSamples <- read.csv("//data-ge02/Users/ftinawi/Documents/Bogoss_directory/testSamples.csv")
transData <- read.csv("//data-ge02/Users/ftinawi/Documents/Bogoss_directory/transData.csv")
```

### Preparing the data

```{r, message=FALSE, warning=FALSE}
#install.packages("plyr")
library(plyr)
#install.packages("dplyr")
library(dplyr)
#install.packages("sqldf")
library(sqldf)
#install.packages("BSDA")
library(BSDA)         # for the z-test function
#install.packages("BEST")

```

We merge the two data sets together:
```{r}
transFull <- merge(x = testSamples, y = transData, by.x = "sample_id", by.y = "sample_id", all.x = TRUE);
transFull[10:20,]
```

Let's see the distribution per transaction type.
```{r}
count(transFull,transFull$transaction_type)
```


### Approximation of the probability distribution 

Grouping in regard to the test type:
```{r}
testGroup <- group_by(testSamples, test_group)
summarise(testGroup,ct=length(test_group))
```

Defining some constants:
```{r, results='hold'}
# Size of the population
n = dim(testSamples)[1]
n
# Size of the test group
m = summarise(testGroup,ct=length(test_group))[[2,2]]
m
```

Since n is large enough, we can estimate p and q as follows:
```{r, results='hold'}
# Estimated probability of being selected in the test group
p <- m/n
p
q <- (1-p)
q
```


Validate conditions to approximate binomial with normal distribution:

```{r, results='hold'}
n*p > 10
n*q > 10
```

Using the Central limit theorem and $Z = \frac{X -\mu}{\sigma}$, we have the following normal distribution $N\sim (14835,105.6)$.

```{r, results='hold'}
mu <- n*p
mu
sig <- sqrt(n*p*q)
sig
```

We plot the graph of the curve.
```{r}
x <- seq(mu - 500,mu + 500, by = 5)
y <- dnorm(x, mean = mu, sd = sig)
plot (x, y, type = "l", xlab = "Z values", ylab = "Density", main = "Graph of normal distribution")
```

### Looking into the rebills

We now look deeper into the call-in users and their purchasing habits.

#### Proportion of rebills

We group the rebills and revenues by test type and transaction type.
```{r}
trxGrp <- group_by(transFull, sample_id, test_group, transaction_type)
transFullGrp <- summarise(trxGrp, trxTT = length(sample_id), revTT = sum(transaction_amount))
head(transFullGrp,15)
```

Let's compute the ratio of call-in users that lead to at least one rebill.
```{r,results='hold'}
CallWithRebill <- dim(transFullGrp[which(transFullGrp$test_group == 1 & transFullGrp$transaction_type == 'REBILL'),])[1]
CallWithRebill
CallWithRebill / m
```

We compare with the web-form users.
```{r,results='hold'}
WebWithRebill <- dim(transFullGrp[which(transFullGrp$test_group == 0 & transFullGrp$transaction_type == 'REBILL'),])[1]
WebWithRebill/(n-m)
#We divide the two proportions
(CallWithRebill/m) / (WebWithRebill/(n-m))
```

**Observation**: Call-in users are 5 times more likely to generate a rebill versus the web form users.  
Is this observation statistically significant?

Let the null hypothesis be:

$H_{0}$ = proportion of rebills from call-in users is similar than the one from users using the web form

and the alternate hypothesis:

$H_{a}$ = proportion of rebills from call-in users is greater than the one from users using the web form

we apply the Z-test:
```{r}
res <- prop.test(c(CallWithRebill,WebWithRebill), c(m,n-m), alternative = "greater")
res
# we verify that the p-value is less than the significance level of 5%
res$p.value < 0.05
```

With a p-value smaller than 2.2e-16 and well below the 5% significance level, we reject the null hypothesis.

**Conclusion**: we can state that call-in users will generate more rebills than web-form users with 95% confidence.  

#### Average revenue per user

We define some useful values:
```{r, results='hold'}
# Denormalized dataframe with rebills and revenues per user
trxDenorm <- sqldf("select sample_id, test_group, count(*) ct_tt
        , ifnull(sum(t.transaction_type == 'REBILL'),0) as ct_rebill
        , ifnull(sum(t.transaction_type == 'CHARGEBACK'),0) as ct_chgbk
        , ifnull(sum(t.transaction_type == 'REFUND'),0) as ct_refund
        , ifnull(sum(t.transaction_amount),0) revenues
        , round(sum(t.transaction_type == 'CHARGEBACK') / sum(t.transaction_type == 'REBILL'), 4) chgbk_rate
        from transFull t
        group by t.sample_id, test_group")
head(trxDenorm)
```

Let's investigate now the revenue average and standard deviation among the two groups.
```{r,results='hold'}
CallAvgRev <- mean(trxDenorm$revenues[trxDenorm$test_group == 1])
CallAvgRev 
WebAvgRev <- mean(trxDenorm$revenues[trxDenorm$test_group == 0])
WebAvgRev
CallSdRev <- sd(trxDenorm$revenues[trxDenorm$test_group == 1])
CallSdRev
WebSdRev <- sd(trxDenorm$revenues[trxDenorm$test_group == 0])
WebSdRev
```

**Observation**: Call-in users generate revenues three times greater than the web form users.  
Is this observation statistically significant?

Let the null hypothesis be:

$H_{0}$ = average revenue from call-in users is similar to the one from users using the web form

and the alternate hypothesis:

$H_{a}$ = average revenue from call-in users is greater then the one from users using the web form

Using the samples standard deviations to estimate the population standard deviations, we compute the z value: 
$$z = \frac{\overline{x}_1 - \overline{x}_2}{\sqrt{s_1^2/n_1 + s_2^2/n_2}}$$
```{r}
z = (CallAvgRev - WebAvgRev)/sqrt(CallSdRev^2/m + WebSdRev^2/(n-m))
z
# Verify that z is in the confidence interval
z > 1.96
```

**Conclusion**:  we can state that call-in users will generate more revenues than web-form users with 95% confidence.

#### Chargeback rate

Let's compute the chargeback rates.  
In order to do so we only keep the users with at least one rebill. The chargeback ratio wouldn't make sense otherwise.
```{r}
# Only keep users with at list one rebill
trxWithRebill <- trxDenorm[trxDenorm$ct_rebill > 0,]
# There are 2497 users left
dim(trxWithRebill)
```

Compute mean and standard deviation.
```{r,results='hold'}
CallAvgCB <- mean(trxWithRebill$chgbk_rate[trxWithRebill$test_group == 1])
CallAvgCB 
WebAvgCB <- mean(trxWithRebill$chgbk_rate[trxWithRebill$test_group == 0])
WebAvgCB
CallSdCB <- sd(trxWithRebill$chgbk_rate[trxWithRebill$test_group == 1])
CallSdCB 
WebSdCB <- sd(trxWithRebill$chgbk_rate[trxWithRebill$test_group == 0])
WebSdCB 
```

**Observation**: Chargeback rate for call-in users seems higher than for the web form users.  
Is this observation statistically significant?


We apply the z-test:
```{r}
res2 <- z.test(trxWithRebill$chgbk_rate[trxWithRebill$test_group == 1],trxWithRebill$chgbk_rate[trxWithRebill$test_group == 0],sigma.x = CallSdCB, sigma.y = WebSdCB,alternative = "greater",conf.level = 0.95)
res2
```

We verify if the p-value is below the 5% bound.
```{r,results='hold'}
#p-value
res2$p.value
res2$p.value < 0.05
```

Since the p-value is too large, we can't reject the null hypothesis. Therefore, the test is non-conclusive.

**Conclusion**: The data available is not sufficient to determine if a call-in user is more likely to generate a higher chargeback rate. The amount of chargeback being quite low (82 chargebacks only), we suggest to use a larger sample.
